
% Section: CONCLUSION
\section{Summary}
\label{sec__incentvives_conclusion}

We focused in this chapter on the need for an incentive-driven regulation mechanism, 
and identified it as a key component to encourage contribution towards and foster adoption of community clouds. 
We investigated incentive mechanisms for community clouds based on reciprocal resource sharing,
and the results highlight their impact on the efficiency of the system and on regulating the resource assignments. 
The regulation component is implemented in a simulator in order to be able to perform assessments for large scale scenarios. 
With simulation experiments we characterised the behaviour of different settings of the incentive mechanism,
and evaluated the success ratio of requests by the nodes and the resource utilisation. 
We implemented a prototype and deployed it in Guifi.net 
to study the performance of the proposed mechanism under the real world constraints.
We find that effort-based incentive schemes perform well in maintaining a community cloud ecosystem, through ensuring continued contribution by the users.
The understanding gained from these results helps in the 
design of the policies that such incentive mechanism could 
follow in a future platform of real community cloud system. 

\subsection*{Notes}
The results presented in this chapter were accomplished in cooperation 
with my advisor Felix Freitag and 
\"Umit C. B\"uy\"uk\c{s}ahin, a Masters student at UPC~\cite{Buyuksahin2013Thesis}. 
\"Umit did provide relevant contributions to the implementation of the simulator, and the prototype.

The results were published as full papers
	\enquote{\emph{Towards Incentive-based Resource Assignment and Regulation in Clouds for Community Networks}}~\cite{Khan2013TowardsIncentives},
	 in 10th International Conference on Economics of Grids, Clouds, Systems, and Services (GECON 2013),
	 Zaragoza, Spain, September 2013, 
	 and \enquote{\emph{Prototyping Incentive-Based Resource Assignment for Clouds in Community Networks}}~\cite{Khan2014Prototyping},
	 in 28th IEEE International Conference on Advanced Information Networking and Applications (AINA 2014), 
	 Victoria, Canada, May 2014.
An extended version of the work was then published in the article 
	\enquote{\emph{Incentive-based Resource Assignment and Regulation for Collaborative Cloud Services in Community Networks}}~\cite{Khan2015Incentive}, 
	in Journal of Computer and System Sciences 81.8 (Dec. 2015).