% definitions.tex

\section{Definitions}
\label{sec__Definitions}

We start by introducing the terms used throughout this chapter and the rest of the thesis.


\paragraph{Community Network Cloud}
Community network clouds get formed when cloud services are provisioned using resources contributed by the 
members of the community network to build services and applications of local interest.
In this thesis, we often use the term community clouds interchangeably 
for community network clouds, 
unless otherwise stated which will be clear from the context.

\paragraph{Dominant Strategy} A strategy is dominant for a player 
when it provides better utility to her than any other strategy, 
no matter what strategy other players choose.

\paragraph{Efficiency}
Efficiency refers to an increased aggregate valuation for all the users.
An optimal solution maximises the social welfare in the system.

\paragraph{Ex Post Budget Balance}
Budget balance is the property that after the resources have been allocated the total value paid by users covers the total payments made to the providers.

\paragraph{Ex Post Nash Equilibrium}
Ex post Nash equilibrium means that the system reaches a Nash equilibrium no matter what a scheduling adversary does.

\paragraph{Fairness}
A fair resource allocation assigns each user a share of system resources which is close to its share of total system funding. 
In other words, fairness refers to minimising envy between the users resulting from allocation of resources.
% See Waldspurger1992: p. 110

\paragraph{Free Riding} 
Free riding refers to the situation where users consume public goods or resources 
without any or minimal contributions from their side,
which results in under-provision of these goods or resources.

\paragraph{Incentive Compatibility}
Incentive compatibility means that there is no incentive for any player to lie about her private information. % excerpt from Zheng2014Star paper

\paragraph{Individual Rationality}
Individual-rationality means that every player 
truthfully participating in the allocation is expected to gain no less utility than by not participating. % excerpt from Zheng2014Star paper

%\paragraph{$k$-Resilient Nash Equilibria}

\paragraph{Nash Equilibrium}
A joint strategy involving all players in a game is a Nash equilibrium 
if no player can achieve better utility
by unilaterally deviating, provided all the other players continue
to play their role as suggested by the joint strategy.
% Excerpt from: Distributed Computing Meets Game Theory: Robust Mechanisms for Rational Secret Sharing and Multiparty Computation (p. 65)

\paragraph{Social Welfare}
Social welfare is an aggregate over the utility of all the players in an allocation.

\paragraph{Solution Preference}
Solution preference means that no player has the incentive to fail the algorithm.
Even though players have different preference over the outcomes of an algorithm, 
no player can gain if the algorithm fails and there is no solution.

\paragraph{Strategy Proofness}
Strategy proofness means that the dominant strategy for all the players is to 
report their true valuations to the allocator, 
and therefore no player has any incentive to cheat.

\paragraph{Utility}
Utility function in game theory measures preference over the allocation of resources, 
and represents satisfaction experienced by the players.

\paragraph{Vickrey-Clarke-Groves (VCG) Mechanism} VCG is a generic truthful mechanism for achieving a socially-optimal solution~\cite{Nisan2001}.
It is a generalisation of a Vickrey–Clarke–Groves auction, 
where each individual is charged a \enquote{social cost} equivalent to the harm they cause to other bidders.

\paragraph{Virtual Machines}
Virtual machine (VM) is an emulation of a computer system, 
where hardware resources, like computing, memory, and storage, are packaged as virtual instances.

% Comments from CAT
% TODO: A number of terms that are used throughout the text,
% such as "social welfare", should be introducted in this chapter.