% Based on LLNCS.DEM the demonstration file of the LaTeX macro package from Springer-Verlag for LNCS version 2.4 for LaTeX2e as of 16. April 2010
%
% Moved LNCS Template's code to a separate file
\input{LNCSTemplate/header.tex}
%
%\usepackage{makeidx}  % allows for indexgeneration
%
\begin{document}
%
\frontmatter          % for the preliminaries
%
\pagestyle{headings}  % switches on printing of running heads
\addtocmark{Hamiltonian Mechanics} % additional mark in the TOC
%
%
%
\mainmatter              % start of the contributions
%
\title{Towards Incentive-based Resource Assignment and Regulation in Clouds for Community Networks}
%
\titlerunning{Resource Regulation in Clouds for Community Networks}  
% abbreviated title (for running head) also used for the TOC unless \toctitle is used
%

\author{ Amin M. Khan \and \"Umit C. B\"uy\"uk\c{s}ahin \and Felix Freitag }
%
\authorrunning{A. M. Khan, \"U. C. B\"uy\"uk\c{s}ahin, and F. Freitag} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Amin M. Khan, \"Umit C. B\"uy\"uk\c{s}ahin, and  Felix Freitag}
%
\institute{
    Department of Computer Architecture\\
    Universitat Polit\`ecnica de Catalunya, Barcelona, Spain\\
    \email{ \{mkhan, ubuyuksa, felix\}@ac.upc.edu }\\
}

\maketitle              % typeset the title of the contribution

\begin{abstract}
Community networks are built with off-the-shelf communication equipment aiming to satisfy a community's demand for Internet access and services. These networks are a real world example of a collective that shares ICT resources. But while these community networks successfully achieve the IP connectivity over the shared network infrastructure, the deployment of applications inside of community networks is surprisingly low. Given that community networks are driven by volunteers, we believe that bringing in incentive-based mechanisms for service and application deployments in community networks will help in unlocking its true potential. We investigate in this paper such mechanisms to steer user contributions, in order to provide cloud services from within community networks. From the analysis of the community network's topology, we derive two scenarios of community clouds, the local cloud and the federated cloud. We develop an architecture tailored to community networks which integrates the incentive mechanism we propose. In simulations of large scale community cloud scenarios we study the behaviour of the incentive mechanism in different configurations, where slices of homogeneous virtual machine instances are shared. Our simulation results allow us to understand better how to configure such an incentive mechanism in a future prototype of a real community cloud system, which ultimately should lead to realisation of clouds in community networks.

\keywords{incentive mechanisms, cloud computing, community networks, distributed resource sharing}
\end{abstract}
%

%% *** Introduction
\input{introduction}

%% *** Section: System Model, Architecture and Design
\input{design} 

% *** Section: Evaluation/Experiments
\input{evaluation} 

% *** Section: Related Work
\input{related-work}

% *** Section: Future Work
\input{discussion}

% *** Section: Conclusion
\input{conclusion}

% use section* for acknowledgement
\section*{Acknowledgement}
This work was supported by the European Community Framework Programme~7 FIRE Initiative projects Community Networks Testbed for the Future Internet (CONFINE), FP7-288535, and CLOMMUNITY, FP7-317879. 
Support is also provided by the Universitat Polit\`ecnica de Catalunya BarcelonaTECH and the Spanish Government through the Delfin project TIN2010-20140-C03-01.


%
% ---- Bibliography ----
%
\bibliographystyle{LNCSTemplate/splncs}
\bibliography{Bibliography/references}
%


%\clearpage
%\addtocmark[2]{Author Index} % additional numbered TOC entry
%\renewcommand{\indexname}{Author Index}
%\printindex
%\clearpage
%\addtocmark[2]{Subject Index} % additional numbered TOC entry
%\markboth{Subject Index}{Subject Index}
%\renewcommand{\indexname}{Subject Index}
%\input{subjidx.ind}

\end{document}
