%!TEX root = ../dissertation.tex
% the acknowledgments section

I am hugely indebted to my advisors, Felix Freitag and Luís Rodrigues,
without whose guidance and support, this journey would never have been possible.

I would also like to thank my co-authors 
	\"Umit C. B\"uy\"uk\c{s}ahin (UPC),
	Roger P. Centelles (Guifi),
	Emmanouil Dimogerontakis (UPC),
	Jacek Dominiak (CA Labs),
	Smrati Gupta (CA Labs),
	Mennan Selimi (UPC),
	Leila Sharifi (IST), and
	Xavier Vilaça (INESC-ID),
who were a great pleasure to work with.
I am also thankful to my colleagues at Distributed Systems Groups, 
DSG at UPC and GSD at INESC-ID,
who provided a great work environment, 
and the backdrop from many an insightful discussions.

During the course of my research, I got a chance to interact with many great minds, 
and I appreciate their feedback and insights, notably
	Jörn Altmann (Seoul),
	Roger Baig (Guifi),
%	Bart Braem (Antwerp),
%	Jim Dowling (SICS),
	Gianfranco Giulioni (Chieti-Pescara),
	Leonardo Maccari (Trento),
	Victor Muntes (CA Labs),
	Leandro Navarro (UPC),
	Navaneeth Rameshan (UPC),
	Omer F. Rana (Cardiff),
	Davide Veiga (UPC), and
	Luis Veiga (INESC-ID, IST).
%	Vladimir Vlassov (KTH).
I would like to especially thank Ricardo Pereira (INESC-ID, IST) 
who reviewed an earlier draft of this manuscript and provided valuable suggestions.

On this life long journey of learning, I am lucky to be guided and mentored by many great \emph{teachers} 
on its many twists and turns, 
and I owe to them my contributions and achievements. 
Lastly, I am thankful to my family for their tremendous support.

\vspace*{\fill}

\parasep

\small{
This work was funded by European Commission (EACEA) through the 
	\href{http://eacea.ec.europa.eu/erasmus_mundus/results_compendia/selected_projects_action_1_joint_doctorates_en.php}
	{Erasmus Mundus doctoral fellowship}, via 
	\href{http://emjd-dc.eu}
	{Erasmus Mundus Joint Doctorate in Distributed Computing (EMJD-DC) programme}.
This work was also supported by European Community Framework Programme~7 FIRE Initiative projects 
	Community Networks Testbed for the Future Internet (CONFINE), FP7-288535, and
	CLOMMUNITY, FP7-317879.
Support was also provided by the Universitat Polit\`ecnica de Catalunya BarcelonaTECH 
and the Spanish Government under contract TIN2013-47245-C2-1-R.
}
